Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-11 article/article.Rmd
Commit 2024-09-11 10:14

\begin{figure}% [h!]
        {\centering
            \subfloat[\label{fig:P-energy-N}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
            \subfloat[\label{fig:P-energy-mean}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
            \subfloat[\label{fig:P-energy-sum}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
        }
    \caption{Time series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
\end{figure}

@@

```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023. The logarithmic color scale denotes the frequency of the respective groups."}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

@@

>>>>

<!--
\begin{figure}% [h!]
        {\centering
            \subfloat[\label{fig:P-energy-N}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
            \subfloat[\label{fig:P-energy-mean}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
            \subfloat[\label{fig:P-energy-sum}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
        }
    \caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
\end{figure}
-->

```{r P-energy, echo=FALSE, fig.cap="Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data."}
knitr::include_graphics("../images/P-energy-complete-multi-3.png")
```

@@

```{r group-2d, echo=FALSE, fig.cap="Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023. The logarithmic color scale denotes the frequency of the respective groups. Note that 19 pints with duration higher than 60 min are not shown."}
knitr::include_graphics("../images/P-groups-bin2d-1.png")
```

@@

# Data availability {.unnumbered}

### 2024-09-11 article/article.tex
Commit 2024-09-11 10:14

\begin{figure}% [h!]
        {\centering
            \subfloat[\label{fig:P-energy-N}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-2} }\\
            \subfloat[\label{fig:P-energy-mean}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-3} }\\
            \subfloat[\label{fig:P-energy-sum}]
                {\includegraphics[width=\linewidth]{../images/P-energy-complete-1} }
        }
    \caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
\end{figure}

@@

\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023. The logarithmic color scale denotes the frequency of the respective groups.}\label{fig:group-2d}
\end{figure}

@@

>>>>

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-complete-multi-3}

\caption{Time-series of (a) the yearly CE number of occurrences, (b) the yearly mean OI and (c) the yearly excess irradiation at Thessaloniki for the period 1994 – 2023. The black lines represent the linear trends on the yearly data.}\label{fig:P-energy}
\end{figure}

@@

\caption{Relation of excess irradiation of CE groups with their duration for Thessaloniki in the period 1994 -- 2023. The logarithmic color scale denotes the frequency of the respective groups. Note that 19 pints with duration higher than 60 min are not shown.}\label{fig:group-2d}
\end{figure}

@@

\hypertarget{data-availability}{%
\section*{Data availability}\label{data-availability}}
\addcontentsline{toc}{section}{Data availability}
